%-------------------------
% Resume in Latex
% Author : Maxim Artemev
% Copied from: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Maksim Artemev}} & Email : \href{mailto:mrartemev.me@gmail.com}{mrartemev.me@gmail.com}\\{Moscow, Russia} & Mobile : +79774097217 \\ & GitHub : \href{https://github.com/MaximArtemev}{MaximArtemev}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Research University Higher School of Economics}{Moscow, Russia}
      {Bachelor of Applied Mathematics and Computer Science}{Sep 2015 -- Jul 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Yandex}{Moscow, Russia}
      {Junior Data Scientist}{Dec 2017 - Sep 2018}
      \resumeItemListStart
        \resumeItem{ \href{https://en.wikipedia.org/wiki/Yandex_Zen}{Yandex Zen}}
        {A personal content feed based on your interests. Machine Learning team. (Python, Java)
          	\begin{itemize}
          		\item Created large block model to feed each text from the news feed to multiple meta classifiers such as topic, tragic and nswf classifier.
          		\item Implemented classifiers joint training increasing f1 score of each class on $\sim$ 10\%.
            	\item Improved quality on the duplicate text recognition by 7\% using Convolutional Siamese Networks.
          	\end{itemize}
          }
          
        \resumeItem{ \href{https://en.wikipedia.org/wiki/Yandex_Maps}{Yandex Maps}}
          {Detailed maps of the whole world. Computer Vision team. (Python)
          	\begin{itemize}
            	\item Increased accuracy of the 
            	\href{https://www.cs.cmu.edu/~rsalakhu/papers/oneshot1.pdf}{Siamese Convolution Network}
            	    from 85\% to 89\%
            	while working at one-shot-learning topic for worldwide sign detection
          	\end{itemize}
          }
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://cs.hse.ru/en/lambda}{HSE Lambda Laboratory \& CERN}}{Moscow, Russia}
      {Junior Researcher}{Oct 2018 - Present}
      \resumeItemListStart
        \resumeItem{Particle Identification}{Particle classification on Large Hadron Collider}
          {
          	\begin{itemize}
          	    \item Improved quality of Pytorch deep model from 95\% to 98\% average ROC-AUC on particle classification.
          	    \item Accelerated classification by 6 times using bayesian inference.
          	\end{itemize}
          }
        \resumeItem{RICH}{Detector response generation at Large Hadron Collider}
          {
          	\begin{itemize}
          	    \item Building GANs with Cramer distance using Tensorflow.
          	\end{itemize}
          }
      \resumeItemListEnd
      
    \resumeSubheading
      {\href{https://www.facebook.com/moscoding}{Moscow Coding School}}{Moscow, Russia}
      {Teacher}{Feb 2018 - Jul 2018}
      \resumeItemListStart
        \resumeItem{Machine Learning Teacher}
          {
          	\begin{itemize}
          	    \item Created semester course about machine learning and data science for 10-11 graders.
          	    \item Prepared and maintained two Kaggle Inclass competitions in the field of natural language processing and computer vision.
          	\end{itemize}
          }
      \resumeItemListEnd

      
    \resumeSubHeadingListEnd
    
%-----------Hackathons-----------------
\section{Additional Experience}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://hackjunction.com}{Junction}}
      {
      	The biggest Europe hackathon.
        \begin{itemize}
            \item Winner of the "Summarizing News" challenge, the best project at AI section
        \end{itemize}
      }
    \resumeSubItem{Teachers Assistant}
      {
        Data analysis in international relations
        \begin{itemize}
            \item Teaching about data science at \href{https://www.hse.ru/en/news/admission/207148580.html}{HSE Data Culture course}
        	\item Prepared and maintained Kaggle Inclass competition about data analysis
        \end{itemize}
      }
  \resumeSubHeadingListEnd



%--------ADDITIONAL EXPERIENCE------------
\section{Additional Skills}
 \resumeSubHeadingListStart
 %\itemsep-0.1em
    \item \textbf{Programming languages:}{
    \begin{itemize}
    	\item {\textbf{Python(Proficient)}, Java, C++, JavaScript, Bash}
    \end{itemize} 
    }
    \item \textbf{Languages:}{
    \begin{itemize}
    	\item {English - Advanced, Russian - Native}
    \end{itemize}
    }
    
    \item \textbf{Technologies:}{ Jupyter Notebook, PyTorch, TensorFlow, Keras, Data Science stack}

 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
