%-------------------------
% Resume in Latex
% Author : Maxim Artemev
% Copied from: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Maksim Artemev}} & Email : \href{mailto:mrartemev@edu.hse.ru}{mrartemev@edu.hse.ru}\\{Moscow, Russia} & Mobile : +7 977 409 7217 \\ & GitHub : \href{https://github.com/MaximArtemev}{github.com/MaximArtemev}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Research University Higher School of Economics}{Moscow, Russia}
      {Bachelor in Applied Mathematics and Computer Science}{September 2015 -- July 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Yandex}{Moscow, Russia}
      {Junior Data Scientist}{December 2017 - Present}
      \resumeItemListStart
        \resumeItem{ \href{https://en.wikipedia.org/wiki/Yandex_Zen}{Yandex Zen}}
        {
        Zen is the Yandex personal recommendation service. It creates a feed of content that automatically adjusts to the interests of the user.
          	\begin{itemize}
          		\item Created large block model to classify each text from the news feed to minor and major classes.
          		\item Constructed infrastructure around this model, for example now it can learn from new data automatically each day.
            	\item Improved quality on the duplicate recognition by 5\% by using Siamese Networks.
          	\end{itemize}
          }
          
        \resumeItem{ \href{https://en.wikipedia.org/wiki/Yandex_Maps}{Yandex Maps}}
          {
          The service provides detailed maps of the whole world. It includes a search, information about traffic jams, routing and street panoramas. 
          	\begin{itemize}
            	\item Taking part in a team of researchers on computer vision. My topic was one and few - shot learning
            	\item Increased accuracy of the Siamese Convolution model from \href{https://www.cs.cmu.edu/~rsalakhu/papers/oneshot1.pdf}{this} paper from 85\% to 89\%
          	\end{itemize}
          }
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://www.facebook.com/moscoding}{Moscow Coding School}}{Moscow, Russia}
      {Teacher}{February 2018 - Summer 2018}
      \resumeItemListStart
        \resumeItem{Machine Learning Teacher}
          {
          	\begin{itemize}
          	    \item Made one year long course about machine learning and data science for kids.
          	    
          	    \item Starting from basics like linear models and trees it finishes with a big project using computer vision or natural language processing.
          	\end{itemize}
          }
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------Hackathons-----------------
\section{Hackathons}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://hackjunction.com}{Junction}}
      {
      	The biggest Europe hackathon.
        \begin{itemize}
            \item Winner of the "Summarizing News" challenge, the best project at AI section
            \item Char Recurrent Neural Network with Attention mechanism to generate headlines based on the content.
            \item Cluster, summarize and generate headlines for all the events from worldwide news.
        \end{itemize}
      }
    \resumeSubItem{VK Hackathon}
      {
      	One of the largest Russian's hackathons, made by the biggest Russian social network.
        \begin{itemize}
        	\item Winner of the UNESCO section, the best project at Charity section
            \item Char level RNN that can recognize toxic/aggressive messages
        \end{itemize}
      }
  \resumeSubHeadingListEnd

%--------ADDITIONAL EXPERIENCE------------
\section{Additional Skills}
 \resumeSubHeadingListStart
 %\itemsep-0.1em
    \item \textbf{Languages:}{
    \begin{itemize}
    	\item \textbf{Proficient:}{Python}
    	\item {Java, C++, C, JavaScript, Bash}
    	\item {English, Russian}
    \end{itemize} 
    }
    \item \textbf{Technologies:}{ Jupyter Notebook, PyTorch, TensorFlow, Keras, Data Science stack}
	\item \textbf{Others:}{
    \begin{itemize}
    	\item Teaching assistant at the \href{https://www.hse.ru/en/news/admission/207148580.html}{HSE Data Culture course}
    	\item Winner at FBK hackathon with youtube/twitter-bot recognition tech
    	\item Mentor of the winners at CROC’s "School of IT solutions" as a team manager
   	\end{itemize}
	}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
